---
title: "Simple beech mapping"
author: "Anthony Davidson"
date: "13/10/2019"
site: bookdown::bookdown_site
output: bookdown::gitbook
bibliography: ["Beech-forests.bib", "references.bib"]
editor_options: 
  chunk_output_type: console
---

*[full plots coming soon...March 2020]*

# Overview {#over}

_Orginal post by Dominik Schneider_ [CougRstats](https://cougrstats.wordpress.com/)

A couple things to note from others in the field of Spatial/gis. Functions in `R` are undergoing a massive change right now. The old stalwart `sp` has been succeeded by `sf` (simple features), which is compatible with the open geospatial consortium standards. When you are looking for solutions online, make sure you know which data type is being used- **they are not interchangeable.** Key points:

  1. You can convert from `sf` to `sp` with `as(x,'Spatial')` and vice versa with `st_as_sf()`. 
  
  2. Stick with `sf` whenever possible, it is the future. `sf` is designed to be more consistent in syntax, tidy, and feature rich (it does everything `rgdal`, `rgeos`, and `sp` do/did).

  3. `sf` is specific to vector data (points, lines, polygons). Gridded raster data is still served by `raster`. Unfortunately, they are not really compatible so if you need to mix them, you will need to convert your `sf` objects to `sp` objects. This should mostly only be the case for analysis because there are mapping packages that handle both. Keep your eye on `star` as an upcoming successor of the `raster` package.

  4. If you do need to mix vector and raster data, I think it’s still worth doing any vector operations with `sf` and then convert to `sp` at the end. I believe many of the `sf` tools are written in c++ to be as efficient as possible. For polygon/raster conversions, check out [fasterize](https://cran.r-project.org/web/packages/fasterize/) and [spex](https://mdsumner.github.io/spex/index.html) for more efficient implementations that work with `sf`. I often just convert my raster and vector data to tibbles and use the tidyverse tools to do the processing.

The new [Geocomputation with R](https://geocompr.robinlovelace.net) recommend `tmap` because it can handle `sp`, `sf`, and `raster` objects. You will see it’s quite powerful. I encourage you to read the vignettes.

## Approach

After much rearranging and managing projection issues I have found that `crs = 2193` works for all the bits of the figures I would like to use. Below fixes `davidson2020_crs` to `crs = 2193`.

### R libraries needed

```{r eval=TRUE, message=FALSE, warning=FALSE, include=FALSE}
# all these packages can be installed from cran
require(sf) # the spatial workhorse
library(spData) #example spatial data
library(tidyverse) # for general data wrangling
library(tmap)    # for static and interactive maps
library(mapview) # for interactive maps
library(grid) # for putting multiple plot on top of each other
library(cowplot) # for arranging multiple ggplots
library(spDataLarge) # more example spatial data

# sets paths for computers with other software components
# this code block produces an enviroment warning
# but not sure how to sort depenancies still
# Feb2020
# myPaths <- .libPaths("C:/Program Files/R/R-3.6.2/library")
# myPaths <- c(myPaths)
# .libPaths(myPaths)  # add new path
# .libPaths()
map.bounds <- tidykml::kml_bounds("./data/research/doc.kml")
map.info <- tidykml::kml_info("./data/research/doc.kml")
tidy.kat <- tidykml::kml_points("./data/research/doc.kml")
tidy.poly <- tidykml::kml_polygons("./data/research/doc.kml")
tidy.read <- tidykml::kml_read("./data/research/doc.kml")

# st_read("./data/research/doc.kml")
```

```{r eval=TRUE, message=FALSE, warning=FALSE, include=FALSE}
#startup only on uni PC
#Anthony
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
require(SFtools)# load some spatial data. 
require(sf)
require(raster)
require(tidyverse)
require(mapview)
require(mapedit)
require(ggplot2)
require(tmap)
require(tmaptools)
require(spData)
require(nzsf)  #issues with this.. #other pckages not upto ...datae??

# fro correct projection
require(sp)
require(spData)
davidson2020_crs <- st_crs(spData::nz)

require(spDataLarge)
```

I will use the new zealand example dataset from `spData`. If you have a csv file with coordinates for points try this general approach and in the points section of this gitbook.

`csvdata <- readr::read_csv(file=`   

**your_filename**

`)`

`sfdata <- sf::st_as_sf(csvdata,` 

and 

`coords = c('xcoords','ycoords'),` 

and then define your

`crs =` `<a_proj4_projection_string>` 

and close the function `)`

```{r echo = TRUE}
# csvdata <- readr::read_csv(file=<your_filename>)
# sfdata <- sf::st_as_sf(csvdata,
#                        coords = c('xcoords','ycoords'),
#                        crs = <a_proj4_projection_string>)
```


### Study areas {.tabset .tabset-fade .tabset-pills}

For this study we had two independent Valley systems. Example datasets in spData include `nz`. It is a multipolygon simple feature collection of New Zealand.

```
spData::nz
## Simple feature collection with 16 features and 6 fields
## geometry type:  MULTIPOLYGON
## dimension:      XY
## bbox:           xmin: 1090144 ymin: 4748537 xmax: 2089533 ymax: 6191874
## epsg (SRID):    2193
## proj4string:    +proj=tmerc +lat_0=0 +lon_0=173 +k=0.9996 +x_0=1600000 +y_0=10000000 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs
```

#### Outline

```{r one-box-plotted, eval=TRUE, message=FALSE, warning=FALSE, include=TRUE, echo = FALSE}
require(sp)
require(spData)
require(tmap)
require(spDataLarge)

nz_map_data <- spData::nz
tmap::tm_shape(nz_map_data) + tm_fill()
# str(nz_map_data)
```

#### Study location

```{r}
require(tidyverse)
require(SFtools)
require(spData)
require(spDataLarge)
require(sf)
# st_crs(spDataLarge::nz_elev)

NZbeech_grids_gps <- tidy.kat[7:18,] %>%
    dplyr::select(folder, name, longitude, latitude) %>%
      transmute(grid = name,
             valley = factor(folder),
             lon = longitude,
             lat = latitude)

plot_valley_gps <- NZbeech_grids_gps %>%
                st_as_sf(coords = c("lon", "lat"), crs = 4326)

# plot_valley_gps$geometry
beech_bbox <- plot_valley_gps %>%
  st_transform(crs = st_crs(nz_elev)) %>%
  st_bbox(st_crs(nz_map)) %>% st_as_sfc()

beech_bbox_test <- plot_valley_gps %>%
  st_transform(crs = st_crs(nz_elev)) %>%
  st_bbox(st_crs(nz_map))

# st_crs(nz_elev)
big_bbox <- beech_bbox_test
big_bbox[1] <- beech_bbox_test[1] - 15000
big_bbox[2] <- beech_bbox_test[2] - 15000
big_bbox[3] <- beech_bbox_test[3] + 15000
big_bbox[4] <- beech_bbox_test[4] + 15000

big_bbox <- big_bbox %>% st_as_sfc()
# beech_bbox

tmap::tm_shape(nz_map_data) + tm_fill() +
   tm_shape(big_bbox) +  #here we are adding the little inset box on the overview map 
   tm_borders(lwd = 2, col = "red") 
```

#### By Valley

```{r eval = FALSE}
require(tidyverse)
require(SFtools)
require(spData)
require(spDataLarge)

st_crs(spDataLarge::nz_elev)

NZbeech_grids_gps <- tidy.kat[7:18,] %>%
    dplyr::select(folder, name, longitude, latitude) %>%
      transmute(grid = name,
             valley = factor(folder),
             lon = longitude,
             lat = latitude)

plot_valley_gps <- NZbeech_grids_gps %>%
                st_as_sf(coords = c("lon", "lat"), crs = 4326)
# 
# %>%
  st_crs(nzsf::proj_nzsf())

beech_bbox <- plot_valley_gps %>%
  st_bbox()

mapview::mapview(plot_valley_gps)


require(nzsf)

# CRS(nz_elev)

# p_south <- 
  ggplot() +
  plot_depth(colour = "lightblue") +
  plot_marine_reserves(fill = "red", colour = "red") +
  plot_qma(qma = "CRA", fill = NA)
  
  
  +
  geom_sf(data = beech_bbox,fill = "darkgreen", colour = NA, size = 0.3, alpha = 0.7)
  # plot_coast(fill = "darkgreen", colour = NA, size = 0.3, alpha = 0.7) +
  # annotation_north_arrow(location = "tl", which_north = "true", style = north_arrow_nautical) +
  # annotation_scale(location = "br", unit_category = "metric") +
  coord_sf(xlim = qma_CRA7_dat[c(1, 3)], ylim = qma_CRA7_dat[c(2, 4)])





plot_valleys_beech<- ggplot() + 
  
  geom_sf(data = nzsf::nz_coastlines_and_islands_polygons_topo_1250k) +
  geom_sf(data = plot_valley_gps, aes(fill = grid, shape = valley, col = grid), size = 4, alpha = 0.5) #+
  
  # coord_sf(xlim = beech_bbox[c(1, 3)], ylim = beech_bbox[c(2, 4)])

plot_valley_gps2 <- NZbeech_grids_gps %>% dplyr::select(valley, lat, lon)%>%
                st_as_sf(coords = c("lon", "lat"), crs = 4193)










###nz snipped section on the nz_hieght crs projection
nz_snipped_region = st_bbox(c(xmin = 1340000, xmax = 1450000,
                      ymin = 5130000, ymax = 5210000), 
crs = st_crs(nz_height)) %>%
  st_as_sfc()

##############################ploting points on sections
require(tmap)
require(tmaptools)
require(spDataLarge)

 nz_height_map = tm_shape(nz_elev, bbox = nz_snipped_region) + 
   tm_raster(style = "cont", palette = "YlGn", legend.show = TRUE) + 
   tm_shape(nz_height) + tm_symbols(shape = 2, col = "red", size = 1) + 
   tm_scale_bar(position = c("left", "bottom")) 
 st_crs(nz_height) 

 nz_height_map
 ## ----08-mapping-18------------------------------------------------------- 
 nz_map = tm_shape(nz)+ tm_polygons()+ tm_borders(lwd = 3)  + 
   # tm_shape(nz_height) + tm_symbols(shape = 2, col = "red", size = 0.1) + 
   tm_shape(egl_bbox)

 nz_map
 
 map_nz = tm_shape(nz) + tm_polygons() 
 class(nz_map)

#<!-- ## ----08-mapping-16------------------------------------------------------- -->
# holly_bbox
plot_holly_valley_gps <- NZbeech_grids_gps %>%
  filter(valley == "Hollyford Valley") %>%
                st_as_sf(coords = c("lon", "lat"), crs = 4326) %>%
                    st_transform(crs = st_crs(nz_height))
holly_bbox <- st_bbox(plot_holly_valley_gps)

# egl_bbox
plot_egl_valley_gps <- NZbeech_grids_gps %>%
  filter(valley == "Eglinton Valley") %>%
                st_as_sf(coords = c("lon", "lat"), crs = 4326) %>%
                    st_transform(crs = st_crs(nz_height))

egl_bbox <- st_bbox(plot_egl_valley_gps, crs = st_crs(nz_height)) %>%
  st_as_sfc()

plot(egl_bbox)


  # ggplot() +
 # tm_shape(nz) + 
map_nz + 
  geom_sf(data = plot_valley_gps, aes(fill = grid, shape = valley, col = grid), size = 4, alpha = 0.5)
 
 # + 
  # geom_sf(nz_elev, aes(fill = ))


# ggplot() +
#   geom_sf(data = grid) +
#   # geom_point(data = datPorts, aes(x = x, y = y), col = "red", size = 2, alpha = 0.6) +
# 
#   # geom_sf_label(data = filter(datPorts, Name == "Dunedin"), aes(label = Name), size =4) +
# 
#   ggtitle("Otago region grids")

#################EGL VALLEY

nz_height_map = tm_shape(nz_elev, bbox = egl_bbox) + 
   tm_raster(style = "cont", palette = "YlGn", legend.show = TRUE) + 
   tm_shape(nz_height) + tm_symbols(shape = 2, col = "red", size = 1) + 
   tm_scale_bar(position = c("left", "bottom")) 
```

#### Grid locations

```{r eval = TRUE}
mapview::mapview(plot_valley_gps)

# tidykml::
#   kml_coords("./data/research/doc.kml")
# 
# tidy.kat[7:18,] %>%
#     dplyr::select(folder, name, longitude, latitude) %>%
#       transmute(grid = name,
#              valley = factor(folder),
#              lon = longitude,
#              lat = latitude)

source("./code/NZbeech_crs_2193.R")
```
