---
title: "A reproducible and uncluttered report of coronavirus for Australians"
author: "[Anthony Davidson](https://github.com/davan690)"
date: "`r format(Sys.time(), '%d %B %Y')`"
site: bookdown::bookdown_site
mail: "dynamicmodellingfromecology@gmail.com"
# !!! linkedin: "yan-holtz-2477534a"
twitter: "antsStats"
github: "apeco2020"
home: "www.ssnhub.com"
# !!! You need to provide a logo image here !!! Or just delete the field for no logo
logo: "logo_gallery.png"
output:
  epuRate::epurate:
    toc: TRUE
    number_sections: FALSE
    code_folding: "hide"
---

```{r, message=FALSE, warning=FALSE}
# sets paths for computers with other software components
# this code block produces an enviroment warning
# but not sure how to sort depenancies still
# Feb2020

# myPaths <- .libPaths("C:/Program Files/R/R-3.6.2/library")
# myPaths <- c(myPaths)
# .libPaths(myPaths)  # add new path
# .libPaths()

library(tidyverse)
library(rmarkdown)    # You need this library to run this template.
library(epuRate)      # Install with devtools: install_github("holtzy/epuRate", force=TRUE)
```

<br><br>

> This website produces a single snapshot of current data on coronavirus. It was built with Australian residents in mind with a reproducible format that allows for the same results to be generated for multiple time intervals. This is the current output as of `r format(Sys.time(), '%d %B %Y')`. This is NOT a conpreheshive list of what to do. This website makes it easier to understand the numbers but all the raw information can be found in the resources.

# Shiny apps for COVID19 {.tabset}
***

## John Coene institute

<iframe src="https://shiny.john-coene.com/coronavirus/" width="100%" height="400px"></iframe>

## `ncov19` package

<iframe src="http://www.bcloud.org/e/" width="100%" height="400px"></iframe>

## COVID-19 Epi Curves

<iframe src="https://simonthelwall.shinyapps.io/covid19/" width="100%" height="400px"></iframe>

Created by Simon Thelwall

## John-Hopkins university

<iframe src="https://ayushpkumar.shinyapps.io/CoronaVirusDashboard/_w_e4c7a489/" width="150%" height="600px"></iframe>

## UK

<iframe src="https://tools.dataatomic.com/shiny/CoronaOutbreak/" width="100%" height="400px"></iframe>

## Switzerland

<iframe src="https://simsc.shinyapps.io/corona/" width="150%" height="400px"></iframe>

## Other `git` repositories

[These sites and new resources are growing by the hour.]("https://github.com/search?l=R&q=covid19&type=Repositories") 

# Data accessed
***

Australia specific data:

<iframe src="https://covid-19.wileam.com/#/AUS" width="150%" height="400px"></iframe>

## Detailed and live??

<iframe src="https://ayushpkumar.shinyapps.io/CoronaVirusDashboard/_w_e4c7a489/" width="150%" height="400px"></iframe>


## Key figures

The data is accessed from the following sources:


Then I explain what is my input data and I load it. Here is how it looks like:

# A few analysis
***

EXAMPLES ONLY FROM TEMPLATE>....

Here are 3 version of a [circular barplot](https://www.r-graph-gallery.com/circular-barplot/) that you can find in the [R graph gallery](https://www.r-graph-gallery.com/circular-barplot/). Note that the figure is centered. You can change the size of the plot with **fig.width** and **fig.height**  



## basic
Let's start with a basic version of a circular representation of the data
```{r, warning=FALSE, fig.align='center' }
# Create dataset
data=data.frame(
  individual=paste( "Mister ", seq(1,60), sep=""),
  value=sample( seq(10,100), 60, replace=T)
)

# Set a number of 'empty bar'
empty_bar=10

# Add lines to the initial dataset
to_add = matrix(NA, empty_bar, ncol(data))
colnames(to_add) = colnames(data)
data=rbind(data, to_add)
data$id=seq(1, nrow(data))

# Get the name and the y position of each label
label_data=data
number_of_bar=nrow(label_data)
angle= 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data$hjust<-ifelse( angle < -90, 1, 0)
label_data$angle<-ifelse(angle < -90, angle+180, angle)

# Make the plot
p = ggplot(data, aes(x=as.factor(id), y=value)) +       # Note that id is a factor. If x is numeric, there is some space between the first bar
  geom_bar(stat="identity", fill="#69b3a2") +
  ylim(-100,120) +
  theme_minimal() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = unit(rep(-1,4), "cm")
  ) +
  coord_polar(start = 0) +
  geom_text(data=label_data, aes(x=id, y=value+10, label=individual, hjust=hjust), color="black", fontface="bold",alpha=0.6, size=2.5, angle= label_data$angle, inherit.aes = FALSE )

p
```


## grouped
```{r, warning=FALSE, fig.align='center' }
# Create dataset
data=data.frame(
  individual=paste( "Mister ", seq(1,60), sep=""),
  group=c( rep('A', 10), rep('B', 30), rep('C', 14), rep('D', 6)) ,
  value=sample( seq(10,100), 60, replace=T)
)

# Set a number of 'empty bar' to add at the end of each group
empty_bar=4
to_add = data.frame( matrix(NA, empty_bar*nlevels(data$group), ncol(data)) )
colnames(to_add) = colnames(data)
to_add$group=rep(levels(data$group), each=empty_bar)
data=rbind(data, to_add)
data=data %>% arrange(group)
data$id=seq(1, nrow(data))

# Get the name and the y position of each label
label_data=data
number_of_bar=nrow(label_data)
angle= 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data$hjust<-ifelse( angle < -90, 1, 0)
label_data$angle<-ifelse(angle < -90, angle+180, angle)

# Make the plot
p = ggplot(data, aes(x=as.factor(id), y=value, fill=group)) +       # Note that id is a factor. If x is numeric, there is some space between the first bar
  geom_bar(stat="identity", alpha=0.5) +
  ylim(-100,120) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = unit(rep(-1,4), "cm")
  ) +
  coord_polar() +
  geom_text(data=label_data, aes(x=id, y=value+10, label=individual, hjust=hjust), color="black", fontface="bold",alpha=0.6, size=2.5, angle= label_data$angle, inherit.aes = FALSE )

p
```

## complex
```{r, warning=FALSE, fig.align='center' }
# Create dataset
data=data.frame(
  individual=paste( "Mister ", seq(1,60), sep=""),
  group=c( rep('A', 10), rep('B', 30), rep('C', 14), rep('D', 6)) ,
  value=sample( seq(10,100), 60, replace=T)
)

# Set a number of 'empty bar' to add at the end of each group
empty_bar=3
to_add = data.frame( matrix(NA, empty_bar*nlevels(data$group), ncol(data)) )
colnames(to_add) = colnames(data)
to_add$group=rep(levels(data$group), each=empty_bar)
data=rbind(data, to_add)
data=data %>% arrange(group)
data$id=seq(1, nrow(data))

# Get the name and the y position of each label
label_data=data
number_of_bar=nrow(label_data)
angle= 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data$hjust<-ifelse( angle < -90, 1, 0)
label_data$angle<-ifelse(angle < -90, angle+180, angle)

# prepare a data frame for base lines
base_data=data %>%
  group_by(group) %>%
  summarize(start=min(id), end=max(id) - empty_bar) %>%
  rowwise() %>%
  mutate(title=mean(c(start, end)))

# prepare a data frame for grid (scales)
grid_data = base_data
grid_data$end = grid_data$end[ c( nrow(grid_data), 1:nrow(grid_data)-1)] + 1
grid_data$start = grid_data$start - 1
grid_data=grid_data[-1,]

# Make the plot
p = ggplot(data, aes(x=as.factor(id), y=value, fill=group)) +       # Note that id is a factor. If x is numeric, there is some space between the first bar

  geom_bar(aes(x=as.factor(id), y=value, fill=group), stat="identity", alpha=0.5) +

  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
  geom_segment(data=grid_data, aes(x = end, y = 80, xend = start, yend = 80), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 60, xend = start, yend = 60), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 40, xend = start, yend = 40), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 20, xend = start, yend = 20), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +

  # Add text showing the value of each 100/75/50/25 lines
  annotate("text", x = rep(max(data$id),4), y = c(20, 40, 60, 80), label = c("20", "40", "60", "80") , color="grey", size=3 , angle=0, fontface="bold", hjust=1) +

  geom_bar(aes(x=as.factor(id), y=value, fill=group), stat="identity", alpha=0.5) +
  ylim(-100,120) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = unit(rep(-1,4), "cm")
  ) +
  coord_polar() +
  geom_text(data=label_data, aes(x=id, y=value+10, label=individual, hjust=hjust), color="black", fontface="bold",alpha=0.6, size=2.5, angle= label_data$angle, inherit.aes = FALSE ) +

  # Add base line information
  geom_segment(data=base_data, aes(x = start, y = -5, xend = end, yend = -5), colour = "black", alpha=0.8, size=0.6 , inherit.aes = FALSE )  +
  geom_text(data=base_data, aes(x = title, y = -18, label=group), hjust=c(1,1,0,0), colour = "black", alpha=0.8, size=4, fontface="bold", inherit.aes = FALSE)

p
```



# Conclusion
***
Read more about this template [here](https://github.com/holtzy/epuRate).

Learn how to custom your R Markdown document [here](https://holtzy.github.io/Pimp-my-rmd/).
